---
title: "Summarizing and plotting US Traffic fatalities with fars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summarizing and plotting US Traffic fatalities with fars}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
library(knitr)
library(fars)
```

# Resources and Goals
`fars` will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. The goal of the package is to provide a monthly summary for the number of fatalities for a specific year as well as plotting a US state map with the coordonates of each traffic fatality over a one year period. 

# Getting the number of monthly traffic fatalities
To retrieve the number of monthly traffic accidents for a specific year(s) we'll use the `fars_summarize_years` function that takes as arguments either a single year or a vector of year values:
```{r get_summary}
fars_summarize_years (c(2013,2014))
```
# Plotting traffic fatalities per year on a US state map
To plot the state map of all traffic fatalities for a specific year we'll use `fars_map_state` function, with the state id as the first argument and the year as the second:
```{r plot_state_map}
fars_map_state(1,2014)
```
